Interpretable Machine Learning for Science \\ with PySR and SymbolicRegression.jl

### 2023-05-01 src/tex/ms.tex
Merge to single ms
Try to fix bibs

This algorithm is computationally efficient and allows for massive paralellization by splitting step~\ref{step:sampling} into groups of individuals which can evolve independently, with asynchronous ``migration'' between the groups.
For the first of the modifications, \we replace the eldest member of a population in step~\ref{step:mutate}, rather than the individual with the lowest fitness, which is known as ``age-regularized'' evolution~\cite{realRegularizedEvolutionImage2019}.
We record the age from the Unix time at which the individual was created during step~\ref{step:mutate}.
Its inclusion in \pysr was motivated by the impressive Neural Architecture Search results of~\cite{realRrealRegularizedEvolutionImage2019,realAutoMLZeroEvolvingMachine2020a} --- though it is worth noting similar regularizations used earlier in SR, e.g.,~\cite{hornbyALPSAgelayeredPopulation2006} and~\cite{schmidtAgefitnessParetoOptimization2010} --- which found this simple modification could prevent early convergence without hurting performance.
This prevents the population from specializing too quickly and getting stuck in a local minima of the search space.
The implementation in~\cite{realAutoMLZeroEvolvingMachine2020a} uses $p=1$ and explores $4\leq n_s \leq 64$, though here \we allow $p$ to be less than $1$, among several other differences.

@@

\bibliographystyle{unsrt85}
\bibliography{Zotero_Library.bib,software.bib}

>>>>

This algorithm is computationally efficient and allows for massive paralellization by splitting step~\ref{step:sampling} into groups of individuals which can evolve independently, with asynchronous ``migration'' between the groups.
For the first of the modifications, \we replace the eldest member of a population in step~\ref{step:mutate}, rather than the individual with the lowest fitness, which is known as ``age-regularized'' evolution~\cite{realRegularizedEvolutionImage2019}.
We record the age from the Unix time at which the individual was created during step~\ref{step:mutate}.
Its inclusion in \pysr was motivated by the impressive Neural Architecture Search results of~\cite{realRegularizedEvolutionImage2019,realAutoMLZeroEvolvingMachine2020a} --- though it is worth noting similar regularizations used earlier in SR, e.g.,~\cite{hornbyALPSAgelayeredPopulation2006} and~\cite{schmidtAgefitnessParetoOptimization2010} --- which found this simple modification could prevent early convergence without hurting performance.
This prevents the population from specializing too quickly and getting stuck in a local minima of the search space.
The implementation in~\cite{realAutoMLZeroEvolvingMachine2020a} uses $p=1$ and explores $4\leq n_s \leq 64$, though here \we allow $p$ to be less than $1$, among several other differences.

@@

\bibliographystyle{unsrt85}
\bibliography{ms}
